Robustly decorrelating errors with mixed quantum gates

### 2019-08-05 decorrelation/mixed_unitaries.tex
removing now old note

% ==============================================================================
% Section: Constructing Useful mixed quantum gates
% ==============================================================================
\section{Constructing mixed quantum gates}
\label{sec:mixed_unitary_processes}
\noindent In this section, we present a methodology for producing useful mixed quantum channels, formalizing the intuitive approach discussed above. As mentioned, our method requires two steps. The first is a control synthesis step, in which we construct an ensemble of gate implementations. Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we use quantum optimal control theory to produce these ensembles. By running simple gradient descent algorithms, such as GRAPE \cite{Khaneja2005}, with different random initial seeds, one can quickly construct large ensembles of approximate quantum gates. We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}. We note that advanced quantum control protocols may provide a more principled approach to control synthesis. DMORPH \cite{dominy2008exploring}, for example, provides a means of exploring continuous families of controls on fidelity level sets, thereby enabling further optimizations against secondary criteria, such as robustness or duration.

@@

One reason to construct an MQG is to improve the worst-case performance of a quantum gate. The worst-case performance is bounded by the diamond distance to the target, which would constitute a natural optimization target.  The diamond distance, however, is a non-linear function that in general requires a convex optimization to compute\cite{watrous2018theory}. This can dramatically slow down iterative optimizers, and so minimizing the diamond distance is a computationally expensive optimization target. However, if the errors are small enough, we can consider a linearized problem, minimizing the diamond distance to first-order in the effective error generator. As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond distance of an MQG with error generators $\{\mathcal{L}_i\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_i \mathcal{L}_i = 0
\end{equation}
\kcy{again with the norm}
In \cite{Campbell2017} Campbell presents an algorithm that, given an oracle that produces approximate unitary operations, will generate controls and weightings to find an MQG with this property. Alternatively, one might consider the following problem: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we are given a collection of precomputed gate implementations. Given such an MQC we can consider the $n^2\times m$ matrix whose columns are the vectorized error generators:
\begin{equation}\label{eq:vectorized_generators}
	\bold{L} = \left(\begin{array}{cccc}
		\mathcal{L}_{1_{1,1}} & \mathcal{L}_{2_{1,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		\mathcal{L}_{1_{n,n}} &  &  \mathcal{L}_{m_{n,n}} \\ 
	\end{array} 	
	\right)
\end{equation}
To satisfy (\ref{eq:campbell-condition}), we can write the sum as a matrix product and solve the following optimization problem, which will be zero if and only if the sum is zero:

>>>>

% ==============================================================================
% Section: Constructing Useful mixed quantum gates
% ==============================================================================
\section{Constructing mixed quantum gates}
\label{sec:mixed_unitary_processes}
\noindent In this section, we present a methodology for producing useful mixed quantum channels, formalizing the intuitive approach discussed above. As mentioned, our method requires two steps. The first is a control synthesis step, in which we construct an ensemble of gate implementations. Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we use quantum optimal control theory to produce these ensembles. By running simple gradient descent algorithms, such as GRAPE \cite{Khaneja2005}, with different random initial seeds, one can quickly construct large ensembles of approximate quantum gates. We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}. We note that advanced quantum control protocols may provide a more principled approach to control synthesis. DMORPH \cite{dominy2008exploring}, for example, provides a means of exploring continuous families of controls on fidelity level sets, thereby enabling further optimizations  fst secondary criteria, such as robustness or duration.

@@

One reason to construct an MQG is to improve the worst-case performance of a quantum gate. The worst-case performance is bounded by the diamond distance to the target, which would constitute a natural optimization target.  The diamond distance, however, is a non-linear function that in general requires a convex optimization to compute\cite{watrous2018theory}. This can dramatically slow down iterative optimizers, and so minimizing the diamond distance is a computationally expensive optimization target. However, if the errors are small enough, we can consider a linearized problem, minimizing the diamond distance to first-order in the effective error generator. As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond distance of an MQG with error generators $\{\mathcal{L}_i\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_i \mathcal{L}_i = 0
\end{equation}
In \cite{Campbell2017} Campbell presents an algorithm that, given an oracle that produces approximate unitary operations, will generate controls and weightings to find an MQG with this property. Alternatively, one might consider the following problem: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we are given a collection of precomputed gate implementations. Given such an MQC we can consider the $n^2\times m$ matrix whose columns are the vectorized error generators:
\begin{equation}\label{eq:vectorized_generators}
	\bold{L} = \left(\begin{array}{cccc}
		\mathcal{L}_{1_{1,1}} & \mathcal{L}_{2_{1,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		\mathcal{L}_{1_{n,n}} &  &  \mathcal{L}_{m_{n,n}} \\ 
	\end{array} 	
	\right)
\end{equation}
To satisfy (\ref{eq:campbell-condition}), we can write the sum as a matrix product and solve the following optimization problem, which will be zero if and only if the sum is zero:
